All the concepts behind TrueSkill Through Time: the \proglang{R}, \proglang{Python} and \proglang{Julia} packages (Draft)

### 2020-10-16 article.tex
Paper TTT: ajustes bibliograf'ia y nuevas abreviaturas de journals

% \en{Probability Theory provides us with a consistent framework for quantifying the uncertainty of our beliefs~\cite{bishop2006-PRML}.}
% \es{La Teor\'ia de la Probabilidad nos proporciona un marco consistente para cuantificar la incertidumbre de nuestras creencias~\citep{bishop2006-PRML}.}
% %
\en{The use of Probability Theory to handle uncertainty, known as Bayesian inference, was widely adopted because it has proven to be a extremely useful tool in practice.}
\es{El uso de la Teor\'ia de la Probabilidad para manejar la incertidumbre, conocida como inferencia bayesiana, se adopt\'o ampliamente porque ha demostrado ser una herramienta extremadamente útil en la pr\'actica.}
%
\en{But this is also a principled choice.}
\es{Esto no es una elecci\'on ad-hoc.}
%
\en{Any system that represent degrees of belief by a numerical value, consistent with classical deductive logic and a set of axioms encoding commonsense reasoning, will necessarily be isomorphic to Probability Theory~\citep{cox1946-reasonableExpectation,vanHorn2003-guideCoxTheorem}.}
\es{Cualquier sistema que represente grados de creencia mediante un valor num\'erico, consistente con la l\'ogica deductiva cl\'asica y un conjunto de axiomas que codifican el razonamiento de sentido común,  ser\'a necesariamente isom\'orfico a la Teor\'ia de la Probabilidad~\citep{cox1946-reasonableExpectation,vanHorn2003-guideCoxTheorem}.}
%
\en{All of the probabilistic inference, no matter how complex, can be solved in terms of two simple equations: the~\ref{eq:sum_rule} and the~\ref{eq:product_rule}.}
\es{Toda inferencia probabil\'istica, no importa cuan compleja ella sea, puede ser resuelta a trav\'es de dos simples ecuaciones: la~\ref{eq:sum_rule} y la~\ref{eq:product_rule}.}

@@

\en{We need a better representation of the temporal process: a single causal model that links all historical activities.}
\es{Necesitamos una mejor representaci\'on del proceso temporal: un único modelo causal que vincule todas las actividades hist\'oricas. }
%
\en{It is difficult to imagine the complex structure that these types of graphical models acquire.}
\es{Es dif\'icil imaginar la compleja estructura que adquieren este tipo de modelos gr\'aficos.}
%
\en{Having a single model allows historical information to propagate throughout the system, solving the decoupling problems mentioned above.}
\es{Contar con un único modelo permite que la informaci\'on hist\'orica propage hacia todo el sistema, resuelviendo los problemas de desacoplamiento antes mencionados.}
%
\en{This is the approach implemented by TrueSkill Through Time~\citep{dangauthier2008-trueskillThroughTime}.}
\es{Este es el enfoque implementado por TrueSkill Through Time~\citep{dangauthier2008-trueskillThroughTime}.}
%
\en{Figure~\ref{fig:smoothing} shows the closest neighbors of a sequence of estimates.}
\es{En la figura~\ref{fig:smoothing} se muestra los vecinos m\'as pr\'oximos de una secuencia de estimaciones.}
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
    \tikz{ %
      \node[latent] (s1) {} ;
      \node[const, above=of s1 ] (ns1) {$s_i^1$} ;
      \node[latent, below=of s1] (p1) {};
      \node[const, right=of p1 ] (np1) {$p_i^1$} ;

@@

% 
% 
% \cite{dangauthier2008-trueskillThroughTime}
% 
% \cite{coulom2008-wholeHistoryRating}
% 
% \cite{maystre2019-pairwise}
% 
% 
% 
% 
% TrueSkill Through Time (TTT) optar por la distribuci\'on normal y ofrece una soluci\'on \'optima.

@@

% \begin{thebibliography}{18}
% \small
% \newcommand{\enquote}[1]{``#1''}
% \providecommand{\natexlab}[1]{#1}
% \providecommand{\url}[1]{\texttt{#1}}
% \providecommand{\urlprefix}{URL }
% \expandafter\ifx\csname urlstyle\endcsname\relax
%   \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
%   \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
%   \urlstyle{rm}\Url}\fi
% \providecommand{\eprint}[2][]{\url{#2}}
% \bibitem[{Bradley and Terry(1952)}]{bradley1952-pairedComparisions}
% Bradley RA, Terry ME (1952).
% \newblock \enquote{Rank analysis of incomplete block designs: I. The method of
%   paired comparisons.}
% \newblock \emph{Biometrika}, \textbf{39}(3/4), 324--345.
% \bibitem[{Cox(1946)}]{cox1946-reasonableExpectation}
% Cox RT (1946).
% \newblock \enquote{Probability, frequency and reasonable expectation.}
% \newblock \emph{American journal of physics}, \textbf{14}(1), 1--13.
% \bibitem[{Dangauthier \emph{et~al.}(2008)}]{dangauthier2008-trueskillThroughTime}
% Dangauthier P, Herbrich R, Minka T, Graepel T (2008).
% \newblock \enquote{Trueskill through time: Revisiting the history of chess.}
% \newblock In \emph{Advances in Neural Information Processing Systems}, pp.
%   337--344.
% \bibitem[{Derex and Mesoudi(2020)}]{derex2020-populationStructure}
% Derex M, Mesoudi A (2020).
% \newblock \enquote{Cumulative Cultural Evolution within Evolving Population
%   Structures.}
% \newblock \emph{Trends in Cognitive Science}.
% \bibitem[{Elo(1961)}]{elo1961-uscf}
% Elo AE (1961).
% \newblock \emph{The USCF rating system}.
% \newblock U.S. Chess Federation publication.
% \bibitem[{Fox(2010)}]{fox2010-bayesianIRT}
% Fox JP (2010).
% \newblock \emph{Bayesian item response modeling: Theory and applications}.
% \newblock Springer Science \& Business Media.
% \bibitem[{Glickman(2013)}]{glikman_gliko_2}
% Glickman M (2013).
% \newblock \enquote{Example of the Glicko-2 system.}
% \newblock \url{http://www.glicko.net/glicko/glicko2.pdf}.
% \newblock Accessed: 2016-07-12.
% \bibitem[{Gonz{\'a}lez-Forero and Gardner(2018)}]{GonzalezForero2018}
% Gonz{\'a}lez-Forero M, Gardner A (2018).
% \newblock \enquote{Inference of ecological and social drivers of human
%   brain-size evolution.}
% \newblock \emph{Nature}, \textbf{557}(7706), 554--557.
% \bibitem[{Herbrich \emph{et~al.}(2006)}]{herbrich2006-trueskill}
% Herbrich R, Minka R, Graepel T (2006).
% \newblock \enquote{TrueSkill: A Bayesian Skill Rating System.}
% \newblock In \emph{Advances in Neural Information Processing Systems 19}, pp.
%   569--576. MIT Press, Cambridge, MA.
% \bibitem[{Herrmann \emph{et~al.}(2007)}]{Herrmann2007}
% Herrmann E, Call J, Hern{\'a}ndez-Lloreda MV, Hare B, Tomasello M (2007).
% \newblock \enquote{Humans have evolved specialized skills of social cognition:
%   The cultural intelligence hypothesis.}
% \newblock \emph{science}, \textbf{317}(5843), 1360--1366.
% \bibitem[{Jones(2011)}]{Jones2011}
% Jones JH (2011).
% \newblock \enquote{Primates and the evolution of long, slow life histories.}
% \newblock \emph{Current Biology}, \textbf{21}(18), R708--R717.
% \bibitem[{Koster \emph{et~al.}(2020)}]{Koster2020}
% Koster J, McElreath R, Hill K, Yu D, Shepard G, Van~Vliet N, Gurven M, Trumble
%   B, Bird RB, Bird D, Codding B, Coad L, Pacheco-Cobos L, Winterhalder B, Lupo
%   K, Schmitt D, Sillitoe P, Franzen M, Alvard M, Venkataraman V, Kraft T,
%   Endicott K, Beckerman S, Marks S, Headland T, Pangau-Adam M, Siren A, Kramer
%   K, Greaves R, Reyes-Garc\'i V, Gu\`eze M, Duda R, Fern\'andez-Llamazares A,
%   Gallois S, Napitupulu L, Ellen R, Ziker J, Nielsen M, Ready E, Healey C, Ross
%   C (2020).
% \newblock \enquote{The life history of human foraging: Cross-cultural and
%   individual variation.}
% \newblock \emph{Science Advances}, \textbf{6}(26), eaax9070.
% \bibitem[{Kschischang \emph{et~al.}(2001)}]{kschischang2001-factorGraphsAndTheSumProductAlgorithm}
% Kschischang FR, Frey BJ, Loeliger HA (2001).
% \newblock \enquote{Factor graphs and the sum-product algorithm.}
% \newblock \emph{IEEE Transactions on information theory}, \textbf{47}(2),
%   498--519.
% \bibitem[{Mosteller(1951)}]{mosteller1951-remarks}
% Mosteller F (1951).
% \newblock \enquote{Remarks on the method of paired comparisons: I, II and III.}
% \newblock \emph{Psychometrika}, \textbf{16}(2).
% \bibitem[{Thurstone(1927)}]{thurstone1927-comparativeJugement}
% Thurstone LL (1927).
% \newblock \enquote{A law of comparative judgment.}
% \newblock \emph{Psychological review}, \textbf{34}(4), 273.
% \bibitem[{van~der Linden(2016)}]{vanDerLinden2016-handbookIRT_1}
% van~der Linden WJ (2016).
% \newblock \emph{Handbook of Item Response Theory, Volume 1: Models}.
% \newblock Chapman and Hall/CRC.
% \bibitem[{Van~Horn(2003)}]{vanHorn2003-guideCoxTheorem}
% Van~Horn KS (2003).
% \newblock \enquote{Constructing a logic of plausible inference: a guide to
%   cox’s theorem.}
% \newblock \emph{International Journal of Approximate Reasoning},
%   \textbf{34}(1), 3--24.
% \bibitem[{Zermelo([1929] 2013)}]{zermelo1929-translation}
% Zermelo E ([1929] 2013).
% \newblock \enquote{The calculation of the results of a tournament as a maximum
%   problem in the calculus of probability (translation of 1929 paper).}
% \newblock In HD~Ebbinghaus, A~Kanamori (eds.), \emph{Ernst Zermelo - Collected
%   Works Volume II}. Springer-Verlag Berlin Heidelberg.
% \newblock ISBN 978-3-540-70856-8.
% \newblock \doi{10.1007/978-3-540-70856-8}.
% \end{thebibliography}

%% -- Appendix (if any) --------------------------------------------------------
%% - After the bibliography with page break.
%% - With proper section titles and _not_ just "Appendix".

>>>>

% \en{Probability Theory provides us with a consistent framework for quantifying the uncertainty of our beliefs~\cite{bishop2006-PRML}.}
% \es{La Teor\'ia de la Probabilidad nos proporciona un marco consistente para cuantificar la incertidumbre de nuestras creencias~\citep{bishop2006-PRML}.}
% %
\en{The use of Probability Theory to handle uncertainty, known as Bayesian inference, was widely adopted because it has proven to be a extremely useful tool in practice.}
\es{El uso de la Teor\'ia de la Probabilidad para manejar la incertidumbre, conocida como inferencia bayesiana, se adopt\'o ampliamente porque ha demostrado ser una herramienta extremadamente útil en la pr\'actica.}
%
\en{But this is also a principled choice.}
\es{Esto no es una elecci\'on ad-hoc.}
%
\en{Any system that represent degrees of belief by a numerical value, consistent with classical deductive logic and a set of axioms encoding commonsense reasoning, will necessarily be isomorphic to Probability Theory~\citep{Cox1946,vanHorn2003-guideCoxTheorem}.}
\es{Cualquier sistema que represente grados de creencia mediante un valor num\'erico, consistente con la l\'ogica deductiva cl\'asica y un conjunto de axiomas que codifican el razonamiento de sentido común,  ser\'a necesariamente isom\'orfico a la Teor\'ia de la Probabilidad~\citep{Cox1946,vanHorn2003-guideCoxTheorem}.}
%
\en{All of the probabilistic inference, no matter how complex, can be solved in terms of two simple equations: the~\ref{eq:sum_rule} and the~\ref{eq:product_rule}.}
\es{Toda inferencia probabil\'istica, no importa cuan compleja ella sea, puede ser resuelta a trav\'es de dos simples ecuaciones: la~\ref{eq:sum_rule} y la~\ref{eq:product_rule}.}

@@

\en{We need a better representation of the temporal process: a single causal model that links all historical activities.}
\es{Necesitamos una mejor representaci\'on del proceso temporal: un único modelo causal que vincule todas las actividades hist\'oricas. }
%
\en{It is difficult to imagine the complex structure that these types of graphical models acquire.}
\es{Es dif\'icil imaginar la compleja estructura que adquieren este tipo de modelos gr\'aficos.}
%
\en{Having a single model allows historical information to propagate throughout the system, solving the decoupling problems mentioned above.}
\es{Contar con un único modelo permite que la informaci\'on hist\'orica propage hacia todo el sistema, resuelviendo los problemas de desacoplamiento antes mencionados.}
%
\en{This is the approach implemented by TrueSkill Through Time~\citep{Dangauthier2007}.}
\es{Este es el enfoque implementado por TrueSkill Through Time~\citep{Dangauthier2007}.}
%
\en{Figure~\ref{fig:smoothing} shows the closest neighbors of a sequence of estimates.}
\es{En la figura~\ref{fig:smoothing} se muestra los vecinos m\'as pr\'oximos de una secuencia de estimaciones.}
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
    \tikz{ %
      \node[latent] (s1) {} ;
      \node[const, above=of s1 ] (ns1) {$s_i^1$} ;
      \node[latent, below=of s1] (p1) {};
      \node[const, right=of p1 ] (np1) {$p_i^1$} ;

@@

% \cite{coulom2008-wholeHistoryRating}
% 
% \cite{maystre2019-pairwise}
% 
% 
% 
% 
% TrueSkill Through Time (TTT) optar por la distribuci\'on normal y ofrece una soluci\'on \'optima.

@@
